### 2021-06-04 text/article_vedrovice.Rmd
add figure placeholders

Another category of variables is derived from retrieved human skeletal remains.
These include biological sex, age simplified into age groups and an indicator
variable as to whether the strontium signal in the remains is of local origin.
The variable representing the recorded sex is simplified into the following
categories: female-sexed body (abbreviated *F*), male-sexed body (*M*),
non-adult (*n. a.*) and undetermined sex (*ind.*).
The age of the body is also simplified into three categories: juveniles (*juv.*)
comprised of the groups *Infans* and *Juvenis*, adults (*ad.*, all bodies aged as *Adultus*)
and mature bodies (*mat.*, anthropological categories *Adultus-Maturus*, *Maturus* and
*Senilis*) and bodies of an undetermined age (*ind.*).
The last category is the indicator for the origin of the buried person.
The local strontium range is defined as two standard deviations from the mean of Sr ranges of
bodies with an age category determined as *Infans*.
Bodies falling within this range are labeled as local, outside the range as non-local;
where data on Sr values is missing, origin is not determined (*ind.*).

@@

@@

By counting the co-occurrences of analyzed variables on simulated data matrices and comparing
the distributions of the statistics proposed by @manly1996 with the values calculated for
the original data set, we can establish whether the overall pattern of artifact
distribution in the graves is non-random and further identify artifacts that deviate
from the random pattern.
The overall deviation from expected co-occurrences, i.e., the *S* statistic
[@manly1996, 475] is significantly large at the 0.05 alpha level.
This suggests that there is strong evidence that the overall distribution of
artifacts in different graves is not random. <!--(see Fig. \@ref(fig:sstat))-->

@@

@@

@@

@@

@@

@@

>>>>

Another category of variables is derived from retrieved human skeletal remains.
These include biological sex, age simplified into age groups and an indicator
variable as to whether the strontium signal in the remains is of local origin.
The variable representing the recorded sex is simplified into the following
categories: female-sexed body (abbreviated *F*), male-sexed body (*M*),
non-adult (*n. a.*) and undetermined sex (*ind.*); see Fig. \@ref(fig:plan-sex).
The age of the body is also simplified into three categories: juveniles (*juv.*)
comprised of the groups *Infans* and *Juvenis*, adults (*ad.*, all bodies aged as *Adultus*)
and mature bodies (*mat.*, anthropological categories *Adultus-Maturus*, *Maturus* and
*Senilis*) and bodies of an undetermined age (*ind.*); see Fig. \@ref(fig:plan-age).
The last category is the indicator for the origin of the buried person.
The local strontium range is defined as two standard deviations from the mean of Sr ranges of
bodies with an age category determined as *Infans*.
Bodies falling within this range are labeled as local, outside the range as non-local;
where data on Sr values is missing, origin is not determined (*ind.*); see Fig. \@ref(fig:plan-orig).

[Figure_04]

[Figure_05]

[Figure_06]

@@

[Figure_09]

@@

By counting the co-occurrences of analyzed variables on simulated data matrices and comparing
the distributions of the statistics proposed by @manly1996 with the values calculated for
the original data set, we can establish whether the overall pattern of artifact
distribution in the graves is non-random and further identify artifacts that deviate
from the random pattern.
The overall deviation from expected co-occurrences, i.e., the *S* statistic
[@manly1996, 475] is significantly large at the 0.05 alpha level.
This suggests that there is strong evidence that the overall distribution of
artifacts in different graves is not random (see Fig. \@ref(fig:sstat)).

[Figure_01]

@@

[Figure_02]

@@

[Figure_03]

@@

[Figure_07]

@@

[Figure_10]

@@

[Figure_11]

@@

[Figure_08]
